I mean really clean the pheno and get to know the hell of the samples

### 2019-10-18 scripts/01_clean_pheno.Rmd
update on the genefamily lefse

```{r}
# the newest pheno table from M
# this sheet have nice sampleids for the samples, and also this is the table has all of the info
phe_M <- read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/CTC Event Table 10162019.xlsx',
                    sheet = 5)
```

>>>>

```{r}
# the newest pheno table from M
# this sheet have nice sampleids for the samples, and also this is the table has all of the info
phe_M <- read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/CTC Event Table 10172019.xlsx',
                    sheet = 5)
```
